%-------------------------
% Resume in LaTeX
% Based on the popular Jake Gutierrez template
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Harshit Srivastava} \\ \vspace{1pt}
    \small +91 7754876626 $|$ \href{mailto:harshitsrv2004@gmail.com}{\underline{harshitsrv2004@gmail.com}} $|$
    \href{https://linkedin.com/in/harshitsrv}{\underline{linkedin.com/in/harshitsrv}} $|$
    \href{https://github.com/hrxsrv}{\underline{github.com/hrxsrv}}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Go, C++} \\
     \textbf{Frameworks/Tools}{: Node.js, Gin, Next.js, AWS} \\
     \textbf{DevOps}{: Docker, CI/CD, Git, Microservices}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology Design and Manufacturing Jabalpur}{2022 -- Present}
      {Bachelor of Technology in Computer Science and Engineering}{CGPA: 8.0/10.0}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern}{August 2025 -- Present}
      {Rimo LLC}{Tokyo, Japan}
      \resumeItemListStart
        \resumeItem{Developed and maintained scalable backend APIs in Go and built reusable UI components using Next.js.}
        \resumeItem{Built a real-time retrieval-augmented suggestion pipeline for live in-meeting question recommendations using a client-side BERT model executed via ONNX Runtime Web with WebGL acceleration.}
        \resumeItem{Implemented in-app notification infrastructure with scheduled cloud triggers and Redis-backed queue-based event delivery.}
        \resumeItem{Reduced legacy API latency by introducing pagination and offloading expensive client-side search operations to Elasticsearch-backed server-side querying.}
      \resumeItemListEnd

    \resumeSubheading
      {Backend Intern}{May 2025 -- August 2025}
      {Connexlab}{Remote}
      \resumeItemListStart
        \resumeItem{Built a real-time AI interviewer platform using LiveKit Agents SDK with OpenAI-powered speech-to-text and text-to-speech pipelines for interactive voice conversations.}
        \resumeItem{Developed an independent YOLO-based frame-by-frame cheat detection microservice for interview proctoring with asynchronous AWS SQS-based event processing.}
        \resumeItem{Designed fault-tolerant distributed worker infrastructure using AWS Fargate Spot workers with dead-letter queues for resilient video analysis and retry handling.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Technical Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Vithos -- AI Health Data Platform} $|$ \emph{Next.js, Express.js, Supabase, Redis, BullMQ} $|$ \href{https://example.com}{\underline{Live}} $|$ \href{https://github.com/hrxsrv}{\underline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Built a multi-tenant platform converting PDF lab reports into a queryable health dataset.}
            \resumeItem{Implemented RAG-based chat using pgvector for semantic retrieval over medical history.}
            \resumeItem{Designed async ingestion pipeline (BullMQ + Redis) with scalable workers for parsing \& embeddings.}
            \resumeItem{Developed biomarker tracking \& trend analytics with dashboards and health nudges.}
            \resumeItem{Ensured secure storage \& sharing via Supabase RLS (DB-level tenant isolation).}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{goComp -- Distributed Code Judge Engine} $|$ \emph{Go, Docker, Redis, REST APIs, Concurrent Worker Pools} $|$ \href{https://github.com/hrxsrv}{\underline{GitHub}}}{}
          \resumeItemListStart
            \resumeItem{Built a distributed online code judge engine in Go with isolated containerized execution environments for secure multi-language code evaluation.}
            \resumeItem{Designed concurrent worker pipelines and execution queues for scalable submission processing with timeout and resource-limit enforcement.}
            \resumeItem{Implemented sandboxed runtime orchestration with Docker-based process isolation, stdout/stderr capture, and deterministic test execution.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards \& Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{MCM Scholarship Recipient (2022--2023)}{ -- Top 1\% academic performance at IIITDM Jabalpur} \\
     \textbf{Convolve (4.0)}{ -- All India Rank 2 (10k+ participants)} \\
     \textbf{Rimo Hack (Tokyo)}{ -- Winner (Rimo teams)} \\
     \textbf{Competitive Programming}{: Codeforces Specialist (1523), CodeChef 4-Star (1624), 300+ algorithmic problems solved}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
